SunPy - Python for Solar Physics

### 2014-01-27 3-5-Database.tex
typo fix
clarify that SQLite is not the default dialect (there is no default at all)

The database sub-package makes use of a SQLite database supported by  
SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}. This library was chosen
since it supports many SQL dialects. The database is stored as a single file which is 
created automatically. This solution makes it possibly to easily backup, copy and distribute
a database file. A server-based database, on the other hand, could be used by a collaboration 
who work together from different machines on the
same data: a central database server stores all data and the clients connect to
it to read or write data.

>>>>

The database sub-package makes use of a database supported by
SQLAlchemy\footnote{\url{http://www.sqlalchemy.org}}. This library was chosen
since it supports many SQL dialects. If SQLite is choosen, the database is stored as a single file which is
created automatically. This solution makes it possibly to easily backup, copy and distribute
a database file. A server-based database, on the other hand, could be used by a collaboration 
who work together from different machines on the
same data: a central database server stores all data and the clients connect to
it to read or write data.
